wpz

### 2023-04-06 src/wpz.Rmd
various outputs

---
title: "diffusion, websites with 1 pc"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(foreach)
library(raster)

options(scipen=10000)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, oa11cd, lsoa11cd, msoa11cd, ladcd, ladnm) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

@@

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

# df %>% filter(is.na(n_by_firm))
# sapply(df %>% left_join(firms), function(x) sum(is.na(x)))
```

@@

```{r}
# get LA for the UK
path.geo <- paste0(path, "/data/raw/Local_Authority_Districts_(December_2021)_UK_BUC.geojson")
la <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

# spatial transformations
la <- spTransform(la, CRS("+init=epsg:4326"))

la.f <- fortify(la, region = "LAD21CD")

# cities
cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)
```

@@

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_la")  # for multiple PC

@@

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(la)
listw <- nb2listw(nb, style = "W", zero.policy = T)

for (t in 1996:2012){
test <- la
test@data <- test@data %>% left_join(df[df$year==t,], by = c("LAD21CD"="ladcd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

@@

mun_merge_new<- merge(test, lmoran, by="LAD21CD")

@@

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc_test", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_la")  # for multiple PC

@@

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(la)
listw <- nb2listw(nb, style = "W", zero.policy = T)

#for (t in 1996:2012){
foreach(t = 1996:2012, .packages = c("tidyverse",
                                     "rgdal",
                                     "rgeos",
                                     "spdep",
                                     "tmap",
                                     "maptools",
                                     "knitr",
                                     "broom")) %dopar% {
test <- la
test@data <- test@data %>% left_join(df[df$year==t,], by = c("LAD21CD"="ladcd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

@@

```{r}
# LA centroids
la.c <- gCentroid(la, byid=TRUE)@coords %>% 
  as.data.frame() %>%
  bind_cols(la@data) %>% 
  dplyr::select(LAD21CD, x, y) %>% 
  remove_rownames()

@@

```{r}
dist <- distm(cbind(la.c$x, la.c$y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist <- round((dist/1000),2) %>% 
  as_tibble()

@@

dist <- dist %>% bind_cols(la.c$LAD21CD) %>% 
  rename(ladcd = last_col()) %>% 
  relocate(ladcd)

@@

# calculate area
la$SHAPE_Area <- area(la) #/ 1000000

# Join with distance and area
df <- df %>% left_join(dist, by = c("ladcd" = "ladcd")) %>% 
  left_join(la@data, by = c("ladcd" = "LAD21CD")) %>% 
  rename(area = SHAPE_Area) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))
```

@@

```{r}
dist.retail <- distm(cbind(la.c$x, la.c$y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail <- round((dist.retail/1000),2) %>% 
  as_tibble()

@@

dist.retail <- dist.retail %>% bind_cols(la.c$LAD21CD) %>% 
  rename(LAD21CD = last_col()) %>% 
  relocate(LAD21CD)

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(LAD21CD, dist.retail)

# Join with complete panel
df <- df %>% left_join(dist.retail, by = c("ladcd" = "LAD21CD"))

@@

@@

for (t in 1996:2012){
  model <- lm(log(n+0.001) ~ log(London), data = df[df$year==t,]) #density
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_la.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_la.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_la.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_la.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/r2_all_la.csv")

r2.all <- dens.London %>% 
  rename(London.LA = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities.LA = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail.LA = rsquared) %>% 
  relocate(year, .before = London.LA) %>% 
  arrange(year)

>>>>

---
title: "wpz"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

Runs all the analysis for the Workplace Zones.

WPZ sources:

- [info](https://www.ons.gov.uk/methodology/geography/geographicalproducts/areaclassifications/2011workplacebasedareaclassification)

- [lookup OA to WPZ](https://geoportal.statistics.gov.uk/datasets/ons::output-area-to-workplace-zone-to-local-authority-district-december-2011-lookup-in-england-and-wales-1/explore)

- [Ireland](https://www.nisra.gov.uk/support/geography/northern-ireland-workplace-zones)

- [Scotland](https://www.data.gov.uk/dataset/02718f33-a1e7-4447-8e04-d305a950c19e/census-2011-workplace-zones)

@@

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)
library(survival)
options(scipen=10000)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, oa11cd) %>% #, lsoa11cd, msoa11cd, ladcd, ladnm
  dplyr::rename(pc = pcds)

path.lookup <- paste0(path,"/data/raw/Output_Area_to_Workplace_Zone_to_Local_Authority_District_(December_2011)_Lookup_in_England_and_Wales.csv")
lookup2 <- read_csv(path.lookup) %>% 
  dplyr::select(OA11CD, WZ11CD) %>% 
  rename(oa11cd = OA11CD)

lookup <- lookup %>% left_join(lookup2) %>% 
  filter(!is.na(WZ11CD)) #%>% 
  #mutate(help = substring(oa11cd, 1, 1)) %>% 
  #filter(is.na(help))
  #distinct(WZ11CD)

rm(lookup2)

# 53,578 unique WZ. OK according to the spatial object, but should be 60,709 according the the WPZ description
```

@@

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, WZ11CD) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

df <- df %>% filter(!is.na(WZ11CD)) %>% 
  complete(WZ11CD, year) %>% 
  replace(is.na(.), 0)

@@

```{r}
# from business census
path.firms <- paste0(path, "/data/raw/business_census2012.csv")
firms <- read_csv(path.firms) %>% #distinct(companystatus) 
  filter(!is.na(postcode),
         companystatus == "Active") %>% 
  dplyr::select(postcode) %>% 
  rename(pc = postcode) %>% 
  left_join(lookup) %>% 
  group_by(WZ11CD) %>% 
  summarise(firms = n())

# firms %>% filter(is.na(oa11cd)) %>% distinct(pc)
# 200k rows and 73k unique postcodes are missing

@@

# df %>% filter(is.na(n_by_firm))
# sapply(df %>% left_join(firms), function(x) sum(is.na(x)))

@@

```{r}
# get LA for the UK
path.geo <- paste0(path, "/data/raw/Workplace_Zones_Dec_2011_GCB_in_England_and_Wales_2022_4617806297229452276.geojson")
wpz <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

# spatial transformations
wpz <- spTransform(la, CRS("+init=epsg:4326"))

wpz.f <- fortify(wpz, region = "LAD21CD")

# cities
cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

# get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- readOGR(path.gb)
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))

@@

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_wpz") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_wpz")  # for multiple PC

@@

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(wpz)
listw <- nb2listw(nb, style = "W", zero.policy = T)

for (t in 1996:2012){
test <- wpz
test@data <- test@data %>% left_join(df[df$year==t,], by = c("wz11cd"="WZ11CD")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

@@

mun_merge_new<- merge(test, lmoran, by="wz11cd")

@@

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a workplace zone") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_wpz") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_wpz")  # for multiple PC

@@

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(wpz)
listw <- nb2listw(nb, style = "W", zero.policy = T)

#for (t in 1996:2012){
foreach(t = 1996:2012, .packages = c("tidyverse",
                                     "rgdal",
                                     "rgeos",
                                     "spdep",
                                     "tmap",
                                     "maptools",
                                     "knitr",
                                     "broom")) %dopar% {
test <- wpz
test@data <- test@data %>% left_join(df[df$year==t,], by = c("wz11cd"="WZ11CD")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a workplace zone") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(wpz, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_wpz.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

@@

```{r}
# LA centroids
wpz.c <- gCentroid(wpz, byid=TRUE)@coords %>% 
  as.data.frame() %>%
  bind_cols(wpz@data) %>% 
  dplyr::select(wz11cd, x, y) %>% 
  remove_rownames()

@@

```{r}
dist <- distm(cbind(wpz.c$x, wpz.c$y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist <- round((dist/1000),2) %>% 
  as_tibble()

@@

dist <- dist %>% bind_cols(wpz.c$wz11cd) %>% 
  rename(wz11cd = last_col()) %>% 
  relocate(wz11cd)

@@

# calculate area
wpz$SHAPE_Area <- area(wpz) #/ 1000000

# Join with distance and area
df <- df %>% left_join(dist, by = c("WZ11CD" = "wz11cd")) %>% 
  left_join(wpz@data, by = c("WZ11CD" = "wz11cd")) %>% 
  rename(area = SHAPE_Area) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)
sapply(df, function(x) sum(is.na(x)))
```

@@

```{r}
dist.retail <- distm(cbind(wpz.c$x, wpz.c$y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail <- round((dist.retail/1000),2) %>% 
  as_tibble()

@@

dist.retail <- dist.retail %>% bind_cols(wpz.c$wz11cd) %>% 
  rename(wz11cd = last_col()) %>% 
  relocate(wz11cd)

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(wz11cd, dist.retail)

# Join with complete panel
df <- df %>% left_join(dist.retail, by = c("WZ11CD" = "wz11cd"))

@@

Classification

library(readxl)
library(httr)
url.classes <- "https://www.ons.gov.uk/file?uri=/methodology/geography/geographicalproducts/areaclassifications/2011workplacebasedareaclassification/classificationofworkplacezonesfortheukdatasets/wzassignmentsfinal.xlsx"

GET(url.classes, write_disk(tf <- tempfile(fileext = ".xlsx", tmpdir = paste0(path, "/data/temp"))))

classes.wpz <- read_excel(tf, sheet = 1) %>% 
  rename(WZ11CD= 'Workplace Zone Code',
         supergroup = 'Supergroup Code',
         group = 'Group Code')

df <- df %>% left_join(classes.wpz)
```

@@

for (t in 1996:2012){
  model <- lm(log(n+0.001) ~ log(London) + as.factor(group), data = df[df$year==t,]) #density
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_wpz.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_wpz.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_wpz.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_wpz.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_wpz.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_wpz.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, Workplace Zone") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/r2_all_wpz.csv")

r2.all <- dens.London %>% 
  rename(London.wpz = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities.wpz = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail.wpz = rsquared) %>% 
  relocate(year, .before = London.wpz) %>% 
  arrange(year)
